Scale Space Edge Detection

### 2018-03-05 paper.tex
updates

    % Set the lstlistings to the Julia color scheme
    \lstset{
        basicstyle=\ttfamily,
        columns=fullflexible,
        frame=single,
        breaklines=true,
        language         = Julia,
        basicstyle       = \ttfamily,
        keywordstyle     = \bfseries\color{blue},
        stringstyle      = \color{magenta},
        commentstyle     = \color{ForestGreen},
        showstringspaces = false,
    }

@@

>>>>

    % Set the lstlistings to the Julia color scheme
    \lstset{
        basicstyle       = \ttfamily,
        columns          = fullflexible,
        frame            = single,
        breaklines       = true,
        language         = Julia,
        basicstyle       = \ttfamily,
        keywordstyle     = \bfseries\color{blue},
        stringstyle      = \color{magenta},
        commentstyle     = \color{ForestGreen},
        showstringspaces = false,
        numbers          = left,
        xleftmargin      = 2em,
        framexleftmargin = 2em
    }

@@

    These will be used for computing all the neccessary two dimensional matrix convolutions that we will use throughout the rest of the code. The next step is to then define our range of scales used and which derivative kernels we will be using to compute two dimensional discrete spatial derivatives. The following code shows the definitions for our variables that will be used for all further calculations.

    \begin{lstlisting}
        # Parameters
        gamma = 1
        scales = exp.(linspace(0, log(50), 40))

        # Load the image
        img = float.(ColorTypes.Gray.(testimage("lena_color_512")))

        # Define derivative convolution matrices
        Dy = Array(parent(Kernel.ando5()[1]))
        Dx = Array(parent(Kernel.ando5()[2]))
    \end{lstlisting}
